---
title: "Getting APPG Data"
author: "Ross P. Coron"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
---

Script to extract All-Party Parliamentary Group (APPG) information. For each APPG listed in Parliament's [Register of All-Party Parliamentary Groups](https://www.parliament.uk/mps-lords-and-offices/standards-and-financial-interests/parliamentary-commissioner-for-standards/registers-of-interests/register-of-all-party-party-parliamentary-groups/) (saved locally but could be scraped), extracts information (stored as tables) into a nested list. Script utilises the [18 June 2025 Register](https://publications.parliament.uk/pa/cm/cmallparty/250618/contents.htm) which contains information on 514 individual Groups. 

```{r message=FALSE, warning=FALSE}

library(dplyr)
library(readr)
library(rvest)
library(stringr)
library(purrr)

```


Load in APPG webpages (saved locally).

```{r}

# Get files
files <- list.files(path="./appg_webpages", full.names=TRUE, recursive=FALSE)

# Filter out non-HTML files
files <- files[!grepl("\\.txt$", files)]

# Get APPG names
appg_names <- str_extract(files, "(?<=2025：).*?(?=\\(29_06)") |>
   str_trim()

# Read HTML code as string
html_vector <- lapply(files, read_file)

```


Populate tibble with APPG names and corresponding webpage's HTML code.

```{r}

# Populate dataframe with APPG names and HTML code
raw_appg_df <- tibble(
   name = appg_names,
   html_code = html_vector
)

# Preview HTML code (500 chars)
substr(raw_appg_df$html_code[[1]], 1, 500)

```


Demo: reconstruct webpage from HTML string.

```{r}

tmp_file <- tempfile(fileext = ".html")

writeLines(html_vector[[1]], tmp_file)

# Open in browser
browseURL(tmp_file)

```


Demo: read in APPG's HTML code and extract tables.

```{r}

test_page <- raw_appg_df$html_code[[1]] %>% 
   read_html()

page_tables <- html_table(test_page)
page_tables

```


Main script: extracts APPG information into a nested list. Reads in HTML code corresponding to an APPG's webpage from a dataframe, extracts tables, and plucks values.

```{r}

appg <- list()

# For each row in APPG dataframe
for (n in 1:nrow(raw_appg_df)) {
   
   # Parse HTML and extract tables
   appg_tables <- raw_appg_df$html_code[[n]] %>% 
      read_html() %>% 
      html_table()
   
   # Extract table values
   entry <- "2025-06-18"
   
   appg_name <- pluck(appg_tables, 1, "X2", 1)
   
   appg_purpose <- pluck(appg_tables, 1, "X2", 2)
   
   appg_category <- pluck(appg_tables, 1, "X2", 3)
   
   contact <- pluck(appg_tables, 3, "X1") %>% 
      str_replace_all("\n", "")
   
   most_recent_agm <- as.Date(pluck(appg_tables, 4, "X2", 2), format = "%d/%m/%Y")
   
   published_statement <- pluck(appg_tables, 4, "X2", 3)
   
   reporting_year <- pluck(appg_tables, 4, "X2", 4)
   
   next_rep_deadline <- as.Date(pluck(appg_tables, 4, "X2", 5), format = "%d/%m/%Y")
   
   # Loop through Parliamentarians involved in APPG (number of Parliamentarians varies)
   parliamentarian <- list()
   
   if (length(appg_tables) >= 2 && !is.null(appg_tables[[2]]$X1)) {
      for (m in 3:length(appg_tables[[2]]$X1)) {
         member <- list(
            member_name  = pluck(appg_tables, 2, "X2", m),
            member_party = pluck(appg_tables, 2, "X3", m),
            member_role  = pluck(appg_tables, 2, "X1", m)
         )
         parliamentarian <- c(parliamentarian, list(member))
      }
   }
   
   # Check for benefit information
   benefits <- list()
   val <- pluck(appg_tables, 5, "X1", 2, .default = NA)
   
   # If no benefits, set to FALSE and child items to NA
   if (!is.na(val) && val == "None") {
      benefit_received <- FALSE
      
      benefits <- list(list(
         source      = NA,
         description = NA,
         value       = NA, 
         received    = NA, 
         registered  = NA
      ))
      
   # If benefits received, pluck extract values (number of benefits varies)
   } else {
      benefit_received <- TRUE
      
      if (length(appg_tables) >= 6 && !is.null(appg_tables[[6]]$X1)) {
         for (i in 3:length(appg_tables[[6]]$X1)) {
            benefit <- list(list(
               source      = pluck(appg_tables, 6, "X1", i),
               description = pluck(appg_tables, 6, "X2", i),
               value       = pluck(appg_tables, 6, "X3", i),
               received    = pluck(appg_tables, 6, "X4", i),
               registered  = pluck(appg_tables, 6, "X5", i)
            ))
            benefits <- c(benefits, benefit)
         }
      }
   }
   
   # Combine everything for this APPG
   temp_list <- list(
      appg_name           = appg_name, 
      appg_purpose        = appg_purpose, 
      appg_category       = appg_category,
      parliamentarian     = parliamentarian,
      contact             = contact, 
      most_recent_agm     = most_recent_agm,
      published_statement = published_statement, 
      benefit_received    = benefit_received, 
      benefits            = benefits
   )
   
   # Append to result list
   appg <- c(appg, list(temp_list))
}

appg[[1]]

```   
