---
title: "Getting APPG Data"
output: html_notebook
---

```{r warning=FALSE}

library(dplyr)
library(readr)
library(rvest)
library(stringr)
library(purrr)

```


Load in APPG webpages (stored locally) as HTML strings
```{r warning=FALSE}

raw_appg_df <- tibble(
   name = character(), 
   html_code = character()
)

files <- list.files(path="./appg_html_files", full.names=TRUE, recursive=FALSE)

# Filter out non-HTML files
files <- files[!grepl("\\.txt$", files)]

# Get APPG names
appg_names <- str_extract(files, "(?<=2025：).*?(?=\\(29_06)") |>
   str_trim()

html_vector <- lapply(files, read_file)

```

For demo purposes, reconstitute webpage from HTML string
```{r}

tmp_file <- tempfile(fileext = ".html")
writeLines(html_vector[[2]], tmp_file)

# Open in browser
browseURL(tmp_file)

```

Populate tibble: APPG name and webpage HTML code
```{r}

raw_appg_df <- tibble(
   name = appg_names,
   html_code = html_vector
)

# Preview HTML code (500 chars)
substr(raw_appg_df$html_code[[1]], 1, 500)

```

Read in HTML code and extract tables
```{r}

test_page <- raw_appg_df$html_code[[7]] %>% 
   read_html()

page_tables <- html_table(test_page)
page_tables

```

```{r}
for (n in 1:nrow(raw_appg_df)) {
   
   appg_tables <- (raw_appg_df$html_code[[1]]) %>% 
      read_html() %>% 
      html_table()
   
   entry = "2025-06-18"
   appg_name = pluck(appg_tables, 1, "X2", 1)
   appg_purpose = pluck(appg_tables, 1, "X2", 2)
    appg_category = pluck(appg_tables, 1, "X2", 3)
   
   parliamentarian = list()
   
   for (m in 3:(length(appg_tables[[2]]$X1))) {
      
      new_list = list(
         member_name = pluck(appg_tables, 2, "X2", m),
         member_party = pluck(appg_tables, 2, "X3", m),
         member_role = pluck(appg_tables, 2, "X1", m)
      )
      
      parliamentarian = c(parliamentarian, list(new_list))
      
      contact <- pluck(appg_tables, 3, "X1") %>% 
         str_replace_all(., "\n", "")
      
      most_recent_agm <- as.Date(pluck(appg_tables, 4, "X2", 2), format = "%d/%m/%Y")
      
      published_statement <- pluck(appg_tables, 4, "X2", 3)
      reporting_year <- pluck(appg_tables, 4, "X2", 4)
      next_rep_deadline <- as.Date(pluck(appg_tables, 4, "X2", 5), format = "%d/%m/%Y")
      
      benefits <- list()
      
      if (appg_tables[[5]]$X1[[2]] == "None") {
         
         benefit_received <- FALSE
         
         new_list = list(
            source = NA,
            description = NA,
            value = NA, 
            received = NA, 
            registered = NA
         )
         
         benefits <- list(benefits, list(new_list))
         
      } else {
         benefit_received <- TRUE
         
         for (n in 2:(length(appg_tables[[6]]$X1))) {
            
            new_list = list(
               source = pluck(appg_tables, 5, "X1", n),
               description = pluck(appg_tables, 5, "X2", n),
               value = pluck(appg_tables, 5, "X3", n), 
               received = pluck(appg_tables, 5, "X4", n),
               registered = pluck(appg_tables, 5, "X5", n),
            )
            
            benefits = c(benefits, list(new_list))
         }
      }
   }
   
   appg = list(
      appg_name = appg_name, 
      appg_purpose = appg_purpose, 
      appg_category= appg_category,
      parliamentarian = parliamentarian,
      contact = contact, 
      most_recent_agm = most_recent_agm,
      published_statement = published_statement, 
      benefit_received = benefit_received, 
      benefits = benefits
   )
   
}
   
```   
   
   entry
   name
   purpose
   category
   parliamentarian
   name
   party
   role
   contact
   most_recent_agm
   published_statement
   reporting_year
   next_reporting_deadline
   benefits
   source
   description
   value
   received
   registered
   
   
   